---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---

After fixing the structure of the json file by adding commas as prefix of every line using Sublime Text 3, we then convert it into an R data frame and keep just the success/failure variable. 

```{r,include=FALSE}
rm(list = ls(all = TRUE))
gc(reset = TRUE)

library(jsonlite)

results <- fromJSON("Results.json", simplifyVector = TRUE, flatten = FALSE)
```
### Here sth weird is happening!!! Initially results variable doesn't work. BUT when I re-run it by re-entering it through the console IT WORKS!!! ##

```{r,include=FALSE}
results <- data.frame(matrix(unlist(results), nrow = 107667))
results$X1 <- NULL
names(results) <- c('success')
```
After opening the initial datasets with Notepad++ in order to re-encode the csv files with 'UTF-8 without BOM', we continue with some basic transformatory procedures. 

loading 'Personal Information' and 'Survey' datasets and merging them into 'survey' with the 'results' dataset, after skippind 'id', 'first_name' and 'last_name' and renaming variables

```{r,include=FALSE}
library(readr)

Personal_Information <- read_csv("C:/Users/SONY/Desktop/Final Project/Personal Information.csv", col_types = cols(first_name = col_skip(), id = col_skip(), last_name = col_skip()))

head(Personal_Information)

Survey_Questions <- read_csv("C:/Users/SONY/Desktop/Final Project/Survey Questions.csv", col_types = cols(id = col_skip()))

head(Survey_Questions)

survey <- cbind(Personal_Information,Survey_Questions,results)

names(survey) <- c("age","gender","income","state","resolution_type","outcome_behaviour","tracking_progress","lifestyle_change","alone","money_cost","success")

View(survey)

rm(Personal_Information,Survey_Questions,results)
```

dropping unused factor levels, checking each variable for missing values and removing them

```{r,include=FALSE}
droplevels(survey)

(mis.val.perc <- sapply(survey,function(x){sum(is.na(x))/length(x)})*100)

survey <- na.omit(survey)

sum(is.na(survey))

survey[2:10] <- lapply(survey[2:10],factor)

str(survey)
```

Checking all factor-levels, re-ordering and recoding in order to get homogeneous levels

```{r,include=FALSE}

levels(survey$income)
survey$income <- factor(survey$income,levels = c("<24999","25000-49999","50000-99999","100000-249999",">250000"),ordered = TRUE)

levels(survey$state)

levels(survey$resolution_type)

levels(survey$outcome_behaviour)
survey$outcome_behaviour[survey$outcome_behaviour == "Out-come"] <- "Outcome"

levels(survey$tracking_progress)

levels(survey$lifestyle_change)
survey$lifestyle_change[survey$lifestyle_change == "large"] <- "Large"

levels(survey$alone)

levels(survey$money_cost)
```

creating age groups

```{r,include=FALSE}
for (i in 1:length(survey$age)) {
 
  if (survey$age[i] >= 16 & survey$age[i] <= 24) 
                { survey$age[i] <- "16-24"}
              else if (survey$age[i] >= 25 & survey$age[i] <= 34) 
                { survey$age[i] <- "25-34"}      
              else if (survey$age[i] >= 35 & survey$age[i] <= 44)
                {survey$age[i] <- "35-44"}                                             else if ( survey$age[i] >= 45 & survey$age[i] <= 54)
                { survey$age[i] <- "45-54"}                                            else {survey$age[i] <- "55-65"}
}

survey$age <- as.factor(survey$age)

View(survey)

write.csv(survey,"survey.csv",row.names = FALSE)
```

our response variable is pretty balanced

```{r,include=FALSE}
table(survey$success)
```
