---
output: word_document
---

#Intlall Dataset

This dataset is about MIT international students and where they come from.

# Geospatial HEATMAPS

Installing packages

install.packages("ggplot2")
install.packages("ggmap")

```{r,fig.width=4,fig.height=3}
# Loading libraries
library(ggplot2)
library(ggmap)

# Loading Intlall dataframe
intlall<-read.csv("~/intlall.csv",stringsAsFactors=FALSE)

# Checking the first 6 rows of intlall dataframe
head(intlall)

# Replacing NAs with 0
intlall[is.na(intlall)]<-0

# re-Checking the first 6 rows of the dataframe
head(intlall)

# Loading world-map dataframe
world_map<-map_data("world")

# Checking world-map structure
str(world_map)

# Merging intlall into world_map dataframe
world_map<-merge(world_map,intlall,by.x ="region",by.y="Citizenship")

# re-Checking world_map structure
str(world_map)

# Creating world_map map
ggplot(world_map,aes(x=long,y=lat,group=group))+geom_polygon(fill="white",color="black")+
  coord_map("mercator")
```

This is a wrong world map graph with no meaning due to wrong re-arrangement of observations,
which happened because of the merging of the two dataframes.

```{r,fig.width=4,fig.height=3}
# Re-ordering observations correctly
world_map<-world_map[order(world_map$group,world_map$order),]

# Re-constructing world_map map
ggplot(world_map,aes(x=long,y=lat,group=group))+geom_polygon(fill="white",color="black")+
  coord_map("mercator")
```

As we see there a few missing countries (ie.countries of Africa)
This happens because they have different name in our two initial dataframes.

```{r,fig.width=4,fig.height=3}
# Constructing a student frequency table per country from the intlall dataframe to check which countries
# have different names from the world_map dataframe
table(intlall$Citizenship) 
```

As we see China has a different name in our two datasets.

```{r,fig.width=4,fig.height=3}
# Re-naming intlall's "China(People's Republic of)" into "China" to match with world_map dataframe
intlall$Citizenship[intlall$Citizenship=="China(People's Republic Of)"]<-"China"

# Re-checking intlall's country names
table(intlall$Citizenship)

# Re-merging both dataframes
world_map<-merge(map_data("world"),intlall,by.x="region",by.y="Citizenship")

# Re-ordering observations correctly
world_map<-world_map[order(world_map$group,world_map$order),]

# re-Building map
ggplot(world_map,aes(x=long,y=lat,group=group))+geom_polygon(fill="white",color="black")+
  coord_map("mercator")

# Re-building world_map map by filling it with the number of total students per country
ggplot(world_map,aes(x=long,y=lat,group=group))+geom_polygon(aes(fill=Total),color="black")+
  coord_map("mercator")
```

As we see more students come from America and India.

```{r,,fig.width=4,fig.height=3}
# re-building world_map map by using "orthographic" view
ggplot(world_map,aes(x=long,y=lat,group=group))+geom_polygon(aes(fill=Total),color="black")+
  coord_map("ortho",orientation=c(20, 30, 0))

# View of world-map from another side
ggplot(world_map,aes(x=long,y=lat,group=group))+geom_polygon(aes(fill=Total),color="black")+
  coord_map("ortho", orientation=c(-37, 175, 0))
```