---
output: word_document
---

# Murders Dataset

This dataset is taken from FBI databases and it's about murders that took place in every state of USA.

# Geospatial HEATMAPS

Installing packages

install.packages("maps")
install.packages("ggmap")


```{r,fig.width=4,fig.height=3}
# Load murders dataset
murders <- read.csv("~/murders.csv")

# Checking dataset structure
str(murders)

# Creating USA dataset
library(maps)
library(ggmap)

statesMap<-map_data("state")

# Checking USA dataset
str(statesMap)

# Creating USA map
ggplot(statesMap,aes(x=long,y=lat,group=group))+geom_polygon(fill="white",color="black")+
  coord_map("mercator")

# Adding variable region to murder dataframe so as to merge it with statesMap dataframe
murders$region<-tolower(murders$State)

# Merging by common variable region the two datasets: murders & statesMap 
murderMap<-merge(statesMap,murders,by="region")

# Checking murderMap
str(murderMap)

# USA heatmap with Murders frequency per state
ggplot(murderMap,aes(x=long,y=lat,group=group,fill=Murders))+geom_polygon(colour="black")+
  scale_fill_gradient(low="black",high="red",guide = "legend")
```

As we see in the map, most murders take place in California and Texas.

```{r,fig.width=4,fig.height=3}
# USA heatmap per state population
ggplot(murderMap, aes(x = long, y = lat, group = group, fill = Population)) + geom_polygon(colour = "black") +scale_fill_gradient(low = "black", high = "red", guide = "legend")
```

The murder and population heatmaps are almost similar. California and Texas are the most populated states.
That's why we will create a heatmap representing the murder rate per population, instead of just the number of murders.
```{r,fig.width=4,fig.height=3}
# Creating variable MurderRate
murderMap$MurderRate<-murderMap$Murders/murderMap$Population*100000

# ggplot for USA map with MurderRate frequency per region
ggplot(murderMap,aes(x=long,y=lat,group=group,fill=MurderRate))+geom_polygon(colour="black")+
  scale_fill_gradient(low="black",high="red",guide = "legend")
```

Our heatmap shows low murder-rate in every state but this is wrong as Washington DC is an outlier with an extremely high murder rate.
That's why we will create a heatmap which contains the states with murder rate =< 10.

```{r,fig.width=4,fig.height=3}
# ggplot for USA map with MurderRate>10 frequency per region
ggplot(murderMap,aes(x=long,y=lat,group=group,fill=MurderRate))+geom_polygon(colour="black")+
  scale_fill_gradient(low="black",high="red",guide = "legend",name="Murder Rate per 100k",limits=c(0.9,10))
```

Councluding, Lousiana state has the highest murder rate.