---
output: word_document
---

# MVT Dataset

This dataset is about Motor Vehicle Thefts in USA.

Installing packages

install.packages("ggplot2")
install.packages("maps")
install.packages("ggmap")

```{r,fig.width=4,fig.height=3}
# Loading MVT dataset
mvt<-read.csv("~/MVT.csv", stringsAsFactors=FALSE)

# Checking data frame structure
str(mvt)

# Transforming variable Date into readable R format 
mvt$Date<-strptime(mvt$Date, format="%m/%d/%y %H:%M")

# Extracting Weekday variable from Date variable
mvt$Weekday<-weekdays(mvt$Date)

# Extracting Hour variable from Date variable
mvt$Hour<-mvt$Date$hour

# re-Checking data frame structure
str(mvt)

# Weekday frequency table
table(mvt$Weekday)

# Transforming Weekday frequency table into WeekdayCounts data-frame
WeekdayCounts<-as.data.frame(table(mvt$Weekday))

# Checking WeekdayCounts data-frame structure
str(WeekdayCounts)

# Frequency linegraph of total car robberies per day
library(ggplot2)

ggplot(WeekdayCounts,aes(x=Var1,y=Freq))+geom_line(aes(group=1))
```

As we see the days of the week are mixed and there is no chronological day order.

```{r,fig.width=4,fig.height=3}
# Transforming Var1 into ordered factor
WeekdayCounts$Var1<-factor(WeekdayCounts$Var1,ordered=TRUE,levels=c("Δευτέρα","Τρίτη","Τετάρτη","Πέμπτη",
                                                                    "Παρασκευή","Σάββατο","Κυριακή"))

# Frequency linegraph of robberies per day with chronological order
ggplot(WeekdayCounts,aes(x=Var1, y=Freq))+geom_line(aes(group=1))
```

As we see from both of our graphs most car robberies take place on Friday, in contrast to Sunday.

```{r,fig.width=4,fig.height=3}
# Changing both axis label name
ggplot(WeekdayCounts,aes(x=Var1, y=Freq))+geom_line(aes(group=1))+xlab("Day of the Week")+ylab("Total Motor
Vehicle Thefts")

# Frequency table of robberries per Weekday - Hour
table(mvt$Weekday,mvt$Hour)

# Transforming Weekday-Hour frequency table into DayHourCounts dataframe
DayHourCounts<-as.data.frame(table(mvt$Weekday, mvt$Hour))

# DayHourCounts dataframe structure
str(DayHourCounts)

# Creating numerical variable Hour by transforming factor variable Var2
DayHourCounts$Hour<-as.numeric(as.character(DayHourCounts$Var2))

# Robbery linegraph per Day - Hour
ggplot(DayHourCounts,aes(x=Hour,y=Freq))+geom_line(aes(group=Var1))
```

We can't understand much from this graph as all days are represented by the same colour.

```{r,fig.width=4,fig.height=3}
# Robbery linegraph per Day - Hour with seperate colour for each day and thicker lines
ggplot(DayHourCounts,aes(x=Hour,y=Freq))+geom_line(aes(group=Var1,color=Var1),size=2)
```

As we see most of the car robberies take place during Sunday,Saturday,Monday midnight and Friday at around 10pm. On the other hand, there are less car robberies at around 4am to 5am every day and 5am to 7.5am during weekends. 

```{r,fig.width=4,fig.height=3}
# Same linegraph with more transparent lines
ggplot(DayHourCounts,aes(x=Hour,y=Freq))+geom_line(aes(group=Var1,color=Var1),size=2,alpha=0.5)
```

As we see this linegraph isn't of much help.

# HEAT MAPS

```{r,fig.width=4,fig.height=3}
# Var1 with ordered levels by chronological day sequence
DayHourCounts$Var1<-factor(DayHourCounts$Var1,ordered=TRUE, 
                            levels=c("Δευτέρα","Τρίτη","Τετάρτη","Πέμπτη","Παρασκευή","Σάββατο","Κυριακή"))

# Robberies frequency heatmap per Day- Hour
ggplot(DayHourCounts,aes(x=Hour, y=Var1))+geom_tile(aes(fill=Freq))
```

As we see most of the car robberies take place during Sunday,Saturday,Monday midnight and Friday at around 10pm. On the other hand, there are less car robberies at around 4am to 5am every day and 5am to 7.5am during weekends. 

```{r,fig.width=4,fig.height=3}
# Replacing the name of the Heatmap legend with "Total MV Thefts"
ggplot(DayHourCounts,aes(x=Hour,y=Var1))+geom_tile(aes(fill=Freq))+scale_fill_gradient(name="Total MV Thefts")+theme(axis.title.y=element_blank())

# Changing the colours of the heatmap legend. White for low frequency and red for higher.
ggplot(DayHourCounts, aes(x = Hour, y = Var1)) + geom_tile(aes(fill = Freq))+scale_fill_gradient(name="Total MV Thefts", low="white", high="red") + theme(axis.title.y = element_blank())
```

As we see Friday night is a high risk time for car robbery

# Geospatial HEAT MAPS
```{r,fig.width=4,fig.height=3}
# Loading Chicago map
library(maps)
library(ggmap)

chicago<-get_map(location="chicago",zoom = 11)

# View Chicago map
ggmap(chicago)

# Placing the first 100 robberies on the map of Chicago
ggmap(chicago)+geom_point(data=mvt[1:100,],aes(x=Longitude,y=Latitude))

# Creating LatLonCounts dataframe: car robbery frequency dataframe, by rounding up to 2 decimals the Longitude & Latitude variables
LatLonCounts<-as.data.frame(table(round(mvt$Longitude,2),round(mvt$Latitude,2)))

# LatLonCounts dataframe structure
str(LatLonCounts)

# Renaming Var1 & Var2 into Long & Lat respectively & turning them into numerical variables
LatLonCounts$Long<-as.numeric(as.character(LatLonCounts$Var1))
LatLonCounts$Lat<-as.numeric(as.character(LatLonCounts$Var2))

# Chicago car robbery map with size and colour of points depending on the frequency of robberies
ggmap(chicago)+geom_point(data= LatLonCounts,aes(x=Long,y=Lat,color=Freq,size=Freq))
```

Brighter and Bigger dotpoints on map represent higher car robbery frequency.

```{r,fig.width=4,fig.height=3}
# Setting yellow colour for low frequency and red colour for high
ggmap(chicago)+geom_point(data=LatLonCounts,aes(x=Long,y=Lat,color=Freq,size=Freq))+
  scale_colour_gradient(low="yellow",high="red")

# Using the argument geom_tile so as to create a more typical heatmap
ggmap(chicago)+geom_tile(data=LatLonCounts,aes(x=Long,y=Lat,alpha=Freq),fill="red")
```

