---
title: " Part -B- "
output: word_document
---

# WHO Dataset

This dataset is about world population and several indexes.

Installing packages

install.packages("ggplot2")

```{r,fig.width=4,fig.height=3}
# Removing exponential notation
options(scipen=999)

# Loading WHO dataset
WHO<-read.csv("~/WHO.csv")

# Checking data frame structure
str(WHO)

# Scatterplot GNI-Fertility Rate
plot(WHO$GNI,WHO$FertilityRate)
```

We observe that higher fertility rates are related to low income.

```{r,fig.width=4,fig.height=3}
# Plot GNI-Fertility Rate with points
library(ggplot2)

scatterplot<-ggplot(WHO,aes(GNI,FertilityRate))
scatterplot+geom_point()

# Plot GNI-Fertility Rate with line
scatterplot+geom_line()

# Changing colour, size & shape
scatterplot+geom_point(color="blue",shape=17,size=3)
scatterplot+geom_point(color="darkred",shape=8,size=3)

# Adding title
scatterplot+geom_point(color="blue",shape=17,size=3)+ggtitle("Fertility Rate vs Gross National Income")

# Save plot as variable
FertilityGNIplot<-scatterplot+geom_point(color="blue",shape=17,size=3)+ggtitle("Fertility Rate vs Gross National Income")

# Export plot to PDF
pdf("FertilityGNIplot.pdf")
print(FertilityGNIplot)
dev.off()

# Export plot to SVG
svg("FertilityGNIplot.svg")
print(FertilityGNIplot)
dev.off()

# Plot with dark red colour, stars & title
scatterplot+geom_point(color="darkred",shape=8,size=3)+ggtitle("Fertility Rate vs. Gross National Income")

# Plot which shows the correlation of GNI-Fertility Rate per Region
ggplot(WHO,aes(x=GNI,y=FertilityRate,color=Region))+geom_point()
```

As we see mostly in Africa we find low income correlation and high fertility rate.

```{r,fig.width=4,fig.height=3}
# Plot which shows the correlation of GNI-Fertility Rate per Life Expectancy
ggplot(WHO,aes(x=GNI,y=FertilityRate,color=LifeExpectancy))+geom_point()
```

As we see people who have more children and low income tend to live less than people with less children and higher income.

```{r,fig.width=4,fig.height=3}
# Correlation Plot Fertility Rate - Under 15
ggplot(WHO,aes(x=FertilityRate,y=Under15))+geom_point()
```

As we see our plot approaches more the pattern of a logistic regression line.
This happens because the rate of increase of Under15 variable is smaller than the one of Fertility Rate variable.

```{r,fig.width=4,fig.height=3}
# Correlation Plot log(Fertility Rate) - Under 15 in order to make our line more linear
ggplot(WHO,aes(x=log(FertilityRate),y=Under15))+geom_point()


# Constructing mod: linear regression model
mod<-lm(Under15~log(FertilityRate),data = WHO)
```

As we see our model consists of the predicted variable Under15 and the independent variable Fertility Rate (predictor).

```{r}
# Model summary
summary(mod)
```

As we see R-squared=0.9391 which means that our predictor variable is of high statistical significance.

```{r,fig.width=4,fig.height=3}
# Log(Fertility Rate) - Under 15 Plot with linear regression line
ggplot(WHO,aes(x=log(FertilityRate),y=Under15))+geom_point()+stat_smooth(method = "lm")

# Log(Fertility Rate) - Under 15 Plot with linear regression line and 99% confidence interval
ggplot(WHO,aes(x=log(FertilityRate),y=Under15))+geom_point()+stat_smooth(method = "lm", level = 0.99)

# Correlation Plot log(Fertility Rate) - Under 15 with linear regression line and NO confidence interval
ggplot(WHO,aes(x=log(FertilityRate),y=Under15))+geom_point()+stat_smooth(method = "lm", se=FALSE)

# Correlation Plot log(Fertility Rate) - Under 15 with orange linear regression line
ggplot(WHO,aes(x=log(FertilityRate),y=Under15))+geom_point()+stat_smooth(method = "lm", colour="orange")
```